### 2017-10-01 TF-vldb2018/subsec-Qinc.tex

%\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}.
\sstab{(iii) Node insertions in $\Delta P_{fi}$}.
Node insertions are handled in the same way as edge insertions, by extending \patedgeinsert.

@@

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
So there no matches are found.
\end{example}

@@

\stab{\bf (V) The complete algorithm for pattern updates}.
Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the maximum match relations of $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.

>>>>

%\eetitle{(4) Node insertions in $\Delta P_{fi}$ only}.
\sstab{(iii) Node insertions in $\Delta P_{fi}$}.
Node insertions are handled in a similar way as edge insertions, by extending \patedgeinsert.

@@

\sstab
(2) For $\ball{[\kw{BA_3},2]}$, \comb finds no \kw{SA_i} connecting to \kw{PM_j}, and vice versa.
Hence, no  sensible matches are found.
\end{example}

@@

\stab{\bf (V) The complete algorithm for pattern updates}.
Given $\tilde{M}(P,G)$, \fb, \bfc and \upl, for pattern update $\Delta P$,
algorithm \incp computes the top-k perfect subgraphs for $P \oplus \Delta P$ in $G$ with early return property, and maintains auxiliary structures simultaneously by invoking procedure \identifyaffball, \incmatch and \comb one by one.
